### 2012-03-31 doc/theses/mikula/conclusion.tex
Master thesis: In progress.

\chapter{Conclusion}
The aim of this thesis was to employ XML operations in the XML schema inference. We analyzed several existing methods of the XML schema inference and we searched for methods that utilize some XML operations, only to found one\todo{Jiny vyraz}, which infers keys from XQuery queries.

@@

\todo[inline]{Nejake prehladne zhrnutie plusov a minusov?}

>>>>

\chapter{Conclusion}
The aim of this thesis was to employ XML operations in the XML schema inference. We analyzed several existing methods of the XML schema inference and we searched for methods that utilize some XML operations. We found only one method, inferring keys from XQuery queries.

@@

\todo[inline]{Nejake prehladne zhrnutie plusov a minusov?}
\todo[inline]{testy}

### 2012-03-31 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\subsection{Auxiliary Functions} \label{step_4_auxiliary_functions}
\todo[inline]{Ako je to s osou descendant or self pri hladani join patternov? Orig. metoda o nej explicitne nehovori, ale zrejme pouziva}
\todo[inline]{Ako je to s attribute osou v L cestach join patternov? Atribut predsa moze byt kluc.}
Firstly, we define some auxiliary functions used by algorithms in this chapter.

>>>>

\subsection{Auxiliary Functions} \label{step_4_auxiliary_functions}
Firstly, we define some auxiliary functions used by algorithms in this chapter.
